---
title: "Connecting-with-the-Spotify-API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Connecting-with-the-Spotify-API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = F}
library(spotidy)
```

To make use of this **spotidy** package, you need to create an app at the developer.spotify.com website. For this, follow these steps:

1. Browse to <https://developer.spotify.com/dashboard/applications>.

2. Log in with your Spotify account.

3. Click on 'Create an app'.

4. Pick an 'App name' and 'App description' of your choice and mark the checkboxes.

5. After creation, you see your 'Client Id' and you can click on 'Show client secret` to unhide your 'Client secret'.

6. Use your 'Client id' and 'Client secret' to retrieve a token from the Spotify API. The function get_spotify_api_token() performs all necessary steps with your 'Client id' and 'Client secret' to retrieve a token. Consider to assign this character string to a variable named 'my_token', which is the default value for all spotidy functions that are in need of a token. 


```{r get-token, eval = F}
my_token <- get_spotify_api_token(client_id = "***", client_secret = "***")
```

A token expires after one hour, so be aware that above line needs to be rerun every hour.

******
**From then on, you should you be able to run below code:**
```{r spotidy in practice code, eval = F}
get_album_tracks("6JKkXVEljQJ1wKbRG5MywC")
get_album_tracks("6JKkXVEljQJ1wKbRG5MywC", "raw")

get_album("6JKkXVEljQJ1wKbRG5MywC")
get_album("6JKkXVEljQJ1wKbRG5MywC", "raw")

get_albums("6JKkXVEljQJ1wKbRG5MywC,01sfgrNbnnPUEyz6GZYlt9")
get_albums("6JKkXVEljQJ1wKbRG5MywC,01sfgrNbnnPUEyz6GZYlt9", "raw")

get_artist_albums("00FQb4jTyendYWaN8pK0wa")
get_artist_albums("00FQb4jTyendYWaN8pK0wa", "raw")

get_artist_top_tracks("73ZPfpfg1LBVvDEArK4l5B", "NL")
get_artist_top_tracks("73ZPfpfg1LBVvDEArK4l5B", "NL", "raw")

get_artist("05GsKvp0yKuCyWQMsPAAmB")
get_artist("05GsKvp0yKuCyWQMsPAAmB", "raw")

get_artists("05GsKvp0yKuCyWQMsPAAmB,73ZPfpfg1LBVvDEArK4l5B")
get_artists("05GsKvp0yKuCyWQMsPAAmB,73ZPfpfg1LBVvDEArK4l5B", "raw")

get_track_audio_features("0uQcP7QVoLvaFsORsdrgNh")
get_track_audio_features("0uQcP7QVoLvaFsORsdrgNh", "raw")

get_track("0uQcP7QVoLvaFsORsdrgNh")
get_track("0uQcP7QVoLvaFsORsdrgNh", "raw")

get_tracks_audio_features("0uQcP7QVoLvaFsORsdrgNh,5sNESr6pQfIhL3krM8CtZn")
get_tracks_audio_features("0uQcP7QVoLvaFsORsdrgNh,5sNESr6pQfIhL3krM8CtZn", "raw")

get_tracks("0uQcP7QVoLvaFsORsdrgNh,5sNESr6pQfIhL3krM8CtZn")
get_tracks("0uQcP7QVoLvaFsORsdrgNh,5sNESr6pQfIhL3krM8CtZn", "raw")

search_albums("Norman Fucking Rockwell!")
search_albums("Norman Fucking Rockwell!", "id")
search_albums("Norman Fucking Rockwell!", "raw")

search_artists("Whitney Houston")
search_artists("Whitney Houston", "id")
search_artists("Whitney Houston", "raw")

search_tracks("What a wonderful world")
search_tracks("What a wonderful world", "id")
search_tracks("What a wonderful world", "raw")
```

**You could combine the search and get functions in the following way:**
```{r combining-search-and-get-examples, eval = F}
get_artist_related_artists(search_artists("Ed Sheeran", "id", 1))
get_album_tracks(search_albums("Blackstar", "id", 1))
get_track_audio_features(search_tracks("Video killed the radio star", "id", 1)
```

